A higher order approximate static condensation method for multi-material diffusion problems

### 2018-11-27 num_sec.tex
Motivate discrete l2-norm, polish numerical section

We define \textit{discrete} $\LTwo$\,--\,norm of $v \in \mathbb V_h \subset \LTwoSpace$
\begin{equation}\label{l2}
  \| v \|_{\lTwoSpace} \coloneqq \| P_h\,v \|_{\LTwoSpace},
\end{equation}
where $P_h \coloneqq$ $\LTwo$\,--\,projection operator on the space of piecewise constant
functions on each mesh element~$\bcell \in \bmesh_h$ (or on each~$\mcell \in \mmesh_h$
if $\bcell$ is a  multi-material cell).

The the discretization error $e_h = p - p_h$ is defined as:

\begin{equation*}
  \errlTwo{} =  \|e_h  \|_{\lTwoSpace} = \| P_h\,p - P_h\,p_h \|_{\LTwoSpace} = \| P_h\,p - p_h \|_{\LTwoSpace}
\end{equation*}
\noindent since~$P_h$ is linear and~$p_h \in \mathbb V_h$.  Then the discrete norm of the discretization error is computed as follows:
$$
\errlTwo{} = \left[\sum\limits_{\bcell \in \bmesh_h}\sum\limits_{\mcell\in\mmesh_h(\bcell)} \left(\frac{1}{|\mcell|}\int_{\mcell} p \,{\rm dx} - p_{\mcell}\right)^2|\mcell|\right]^2,
$$
where $|\mcell|$ is
the area of cell $\mcell$.

@@

	\begin{figure}[h]
		\centering
		\begin{subfigure}{.41\linewidth}
			\centering
			\includegraphicsw{err2_asc0.png}
			\caption{$\vect K_1 \equiv \vect K_2 \equiv \vect I$}
			\label{fig:fake:2}
		\end{subfigure}%
		\hfill
		\begin{subfigure}{.41\linewidth}
			\centering
			\includegraphicsw{err3_asc0.png}
			\caption{$\vect K_1 \equiv \vect K_2 \equiv \vect K_3 \equiv \vect I$}
			\label{fig:fake:3}
		\end{subfigure}
		\caption{Material distribution for pseudo-multi-material problem 2-materials(left), 3-materials(right) \label{fig:fake}}		
	\end{figure}

The first set of tests is designed to check the property of the method to accurately recover the solution that is the polynomial of degree~1. Let us consider the diffusion problem~\eqref{dual} with~$c \equiv f \equiv 0$,
$\partial\Omega_D = \partial\Omega$. The computational domain $\Omega=[0,1]^2$
is divided into several subdomains by nonintersecting straight lines.
In these settings the interface reconstruction algorithm MOF reconstructs
the interfaces exactly. To test the {\it linearity preservation} property,
 we set up a pseudo-multi-material problem with the diffusion tensor being the
 same in all subdomains, $\vect K_i = \vect I$ .
 The exact solution a linear function. The geometry of two cases under consideration is shown in Figure~
\ref{fig:fake}.

	We denote
        %the exact pressure solution by~$p$ and
        the solution computed  with the ASC($n$) method by~$p_{h,\,n}$, $n = 0, 1$.

        For ASC(0) we have~$\errlTwo{0} = 6.38 \times 10^{-2}$ and $6.41 \times 10^{-2}$ for the configurations shown in Figures~\ref{fig:fake:2} and~\ref{fig:fake:3}, respectively.
        That is, ASC(0) is not able to recover $P_1$ solutions exactly.

	Since ASC(1) approximates interface traces with $P_1$ functions
        it recovers edge-based degrees of freedom exactly in the sense of mean values. This results in exact reconstruction
        of cell-based unknowns and {\it linearity preservation} property for both examples, i.e.,
	\begin{equation*}
		\errlTwo{1} = \left\| p - p_{h,\,1} \right\|_{\lTwoSpace} = 0.
	\end{equation*}

	%% As we saw in previous section,
        In general, one may not expect concentration and flux convergence to be better than second order with respect to~$\lTwo$\,--\,error for ASC($1$).  However, taking the example above into account, one may expect that convergence of ASC(1) with respect to~$\lTwo$-norm is superior
        to  convergence properties of ASC(0).

@@

        In this set of tests, we consider the diffusion problem~\eqref{dual} with~$c = f = 0$, $\partial\Omega_D = \partial\Omega$,
        and two different materials in the domain.
        $\vect K = k\,\vect I$, $k = 1$ in the left part of the domain and $k = 0.1$ in the right (see Figure~\ref{fig:pwlin:mat}).
        The exact solution is piecewise linear such that the normal flux is continuous across the interface (see Figure~\ref{fig:pwlin:p}).

@@

	For this example we use a sequence of square base\,meshes~$\bmesh_i$, $i = 1, 2, 3, 4$; $h_i \coloneqq$ max diameter of the cell. We denote by
	\begin{equation*}
		\rho_{n,\,i} \coloneqq \frac{\log \errlTwo{n,\,i} / \errlTwo{n,\,i+1}}{\log h_i / h_{i+1}}
	\end{equation*}
the reduction rate order of ASC($n$) in ~$\lTwo$\,-\,norm between $i$ and $i+1$ refinement step. We also compute the $\ell^{\infty}$-norm of the error
	\begin{equation*}
		\errInf{n,\,i} \coloneqq \left\| p - p_{h_i,\,n} \right\|_\infty
	\end{equation*}
	for ASC($n$).

	\begin{table}[h!]\small
		\centering
		\caption{Piecewise linear example: convergence \label{fig:conv:pwlin}}
			\begin{tabular}[1.5]{| c | c || c | c || c |}
				\hline
				\multirow{5}{*}{\rotatebox{90}{ASC(0)}} & $h$ & $\errlTwo{0}$ & $\rho$ & $\errInf{0}$ \\
				\cline{2-5}
				& $3.5\times10^{-1}$ & $7.3\times10^{-1}$ & & 4.8 \\
				\cline{2-5}
				& $8.8\times10^{-2}$ & $1.6\times10^{-1}$ & 1.1 & 1.2 \\
				\cline{2-5}
				& $2.2\times10^{-2}$ & $3.7\times10^{-2}$ & 1.1 & $3.4\times10^{-1}$ \\
				\cline{2-5}
				& $5.5\times10^{-3}$ & $8.9\times10^{-3}$ & 1.0 & $7.9\times10^{-2}$ \\
				\hline
				\hline
				\multirow{5}{*}{\rotatebox{90}{ASC(1)}} & $h$ & $\errlTwo{1}$ & $\rho$ & $\errInf{1}$ \\
				\cline{2-5}
				& $3.5\times10^{-1}$ & $2.5\times10^{-2}$ & & $1.6\times10^{-1}$ \\
				\cline{2-5}
				& $8.8\times10^{-2}$ & $1.9\times10^{-3}$ & 1.84 & $6.3\times10^{-2}$ \\
				\cline{2-5}
				& $2.2\times10^{-2}$ & $1.6\times10^{-4}$ & 1.79 & $9.8\times10^{-3}$ \\
				\cline{2-5}
				& $5.5\times10^{-3}$ & $1.3\times10^{-5}$ & 1.80 & $4.0\times10^{-3}$ \\
				\hline
			\end{tabular}
	\end{table}

	Numerical results are shown in Table~\ref{fig:conv:pwlin}. We observe that ASC(0) converges linearly with respect to $\lTwo$-norm, and ASC(1) has the convergence rate close to quadratic with respect to the $\lTwo$-norm.

@@

	\subsubsection{Two Materials}\label{sec:twomat}

@@

	Let us consider the diffusion problem~\eqref{dual} with~$c = 0$,
        $\partial\Omega_D = \partial\Omega$. The computational domain is divided into
        subdomains: $\Omega_1 = \{ {\bf x} : \|{\bf x} - {\bf x}_0\|< 0.25,~
        {\bf x}_0 = (0.5,0.5)\}$ and  $\Omega_2 = [0,1]^2 / \Omega_1$.
        The diffusion tensor is set  $\vect K_i = k_i\,\vect I$ in $\Omega_i$,
        $k_1 = 0.001$ and $k_2=1$. The exact solution is piecewise quadratic such
        that the normal flux is continuous across the interface (see Figure~\ref{fig:pwquad2}).
        For this problem, we compared convergence properties of the  ASC(0) and ASC(1) methods
        on a sequence of Voronoi meshes.

	\begin{table}[h!]\small
		\centering
		\caption{Piecewise quadratic example, two materials: convergence \label{tab:conv:pwquad2}}
		\begin{tabular}[1.5]{| c | c || c | c || c |}
		  \hline
		  \multirow{7}{*}{\rotatebox{90}{ASC(0)}} & $h$ & $\errlTwo{0}$ & ${\rho}$ & $\errInf{0}$ \\
		  \cline{2-5}
		  & $3.0\times10^{-1}$ & $2.4\times10^{-3}$ & & $6.3\times10^{-1}$ \\
		  \cline{2-5}
		  & $1.5\times10^{-1}$ & $6.5\times10^{-4}$ & 2.0 & $7.0\times10^{-3}$ \\
		  \cline{2-5}
		  & $8.1\times10^{-2}$ & $2.6\times10^{-4}$ & 1.4 & $3.2\times10^{-3}$ \\
		  \cline{2-5}
		  & $4.2\times10^{-2}$ & $1.4\times10^{-4}$ & 0.9 & $2.3\times10^{-3}$ \\
		  \cline{2-5}
		  & $2.1\times10^{-2}$ & $3.7\times10^{-5}$ & 1.9 & $1.1\times10^{-3}$ \\
		  \cline{2-5}
		  & $1.0\times10^{-2}$ & $2.7\times10^{-5}$ & 0.4 & $8.6\times10^{-4}$ \\
		  \hline
		  \hline
		  \multirow{7}{*}{\rotatebox{90}{ASC(1)}} & $h$ & $\errlTwo{1}$ & ${\rho}$ & $\errInf{1}$ \\
		  \cline{2-5}
		  & $3.0\times10^{-1}$ & $2.4\times10^{-3}$ & & $2.1\times10^{-3}$ \\
		  \cline{2-5}
		  & {$1.5\times10^{-1}$} & $7.0\times10^{-4}$ & 1.9 & {$1.3\times10^{-2}$} \\
		  \cline{2-5}
		  & $8.1\times10^{-2}$ & $2.3\times10^{-4}$ & 1.8 & $6.8\times10^{-4}$ \\
		  \cline{2-5}
		  & $4.2\times10^{-2}$ & $6.8\times10^{-5}$ & 1.8 & $3.2\times10^{-4}$ \\
		  \cline{2-5}
		  & $2.1\times10^{-2}$ & $2.0\times10^{-5}$ & 1.8 & $1.1\times10^{-4}$ \\
		  \cline{2-5}
		  & $1.0\times10^{-2}$ & $5.4\times10^{-6}$ & 1.9 & $3.3\times10^{-5}$ \\
		  \hline
		\end{tabular}
	\end{table}

@@

        We also observe a bump in the max norm error for ASC(1) on the second mesh level,
        $h = 1.5\times10^{-1}$. To have some insight, we show the corresponding mesh in the Figure~\ref{fig:conv:pwquad2:inf:mesh}.
        One may note that the interface reconstruction produces significant discontinuity of
        interfaces: A small volume of the external material, i.e. the one occupying $\Omega_2$ domain, appears
        inside the disk, domain $\Omega_1$. Due to constant trace approximation, ASC(0)
        is not sensitive to such  irregularity. It turns out that for  ASC(1) the $\ell^\infty$ norm of the error is affected by  the appearance of such small isolated cut cells. At the same time, this  %as expected,
        does not affect the $\lTwo$-convergence of ASC(1).

        \begin{figure}
		\centering
		\label{fig:conv:pwquad2:inf}
		\begin{subfigure}{.29\linewidth}
			\centering
			\includegraphicsw{circle_voronoi_2_mat.png}
			\caption{Materials}
			\label{fig:conv:pwquad2:inf:mesh}
		\end{subfigure}%
\hskip1ex
		\begin{subfigure}{.33\linewidth}
			\centering
			\includegraphicsw{circle_voronoi_2_asc0.png}
			\caption{ASC(0), $p_h$}
		\end{subfigure}%
\hskip1ex
		\begin{subfigure}{.33\linewidth}
			\centering
			\includegraphicsw{circle_voronoi_2_asc1.png}
			\caption{ASC(1), $p_h$}			
		\end{subfigure}%
\caption{Piecewise quadratic example, two materials: $h = 1.5\times10^{-1}$. This figure illustrates the appearance of small isolated material volumes during numerical reconstruction of material interfaces. This may affect the $\ell^\infty$ error norm of the ASC(1).}
	\end{figure}

%	\clearpage

	\subsubsection{Three Materials}\label{sec:threemat}

@@

	In the next group of numerical tests, we consider the same  diffusion problem~\eqref{dual}
        with~$c = 0$, $\partial\Omega_D = \partial\Omega$. The computational domain is now
        divided into three subdomains: $\Omega_1 = \{{\bf x} : \|{\bf x} - {\bf x}_0\| < 0.2$,
        $\Omega_2 = \{{\bf x} : 0.2 \le \|{\bf x} - {\bf x}_0\| < 0.25$, and
        $\Omega_3 = [0,1]^2 / (\Omega_1\cup\Omega_2)$. The diffusion tensor is set to be
        $\vect K_i = k_i\,\vect I$, $k_{1} = k_{3} = 1$, $k_2 = 0.001$.
        The geometry represents a ring with $k_2=0.001$ inside the ring and $k_{1} = k_{3} = 1$ outside
        the ring. The exact solution is piecewise quadratic such that the normal flux is
        continuous across the interface; see Figure~\ref{fig:pwquad3}.
        We use a sequence of triangular meshes to study convergence for this example. In this set of tests, we also consider the numerical method based on homogenization techniques for the comparison. The homogenization method we use is from \cite{dawes2013solving}. The homogenized values of the diffusion tensor are computed on the base cells $\bcell$ and then plugged into the MFD discretization applied on the  base mesh $\bmesh_h$; see \cite{kikinzon2017approximate} for implementation details of this method.

>>>>

Let $h$ be a max cell diameter for the macro-mesh~$\bmesh_h$, and $\mathbb V_h \subset \LTwoSpace$ be a space of piecewise constant
functions on each cell~$\mcell \in \mmesh(\bcell)$, $\bcell \in \bmesh_h$. We define \textit{discrete} $\LTwo$-norm of $v \in \LTwoSpace$ as
\begin{equation}\label{l2}
  \| v \|_{\lTwoSpace} \coloneqq \| P_h\,v \|_{\LTwoSpace},
\end{equation}
where $P_h\;:\;\LTwoSpace\rightarrow\mathbb V_h$ is $\LTwo$-projection operator.

For the error~$e_h \coloneqq p - p_h$ between the exact and computed solutions we have
\begin{equation}\label{l2norm}
	\errlTwo{h} \coloneqq \| e_h \|_{\lTwoSpace} = \| p - p_h \|_{\lTwoSpace} = \| P_h\,p - P_h\,p_h \|_{\LTwoSpace} = \| P_h\,p - p_h \|_{\LTwoSpace}
\end{equation}
since~$P_h$ is linear and~$p_h \in \mathbb V_h$. The discrete norm~\eqref{l2norm} of the discretization error is computed as follows:
$$
	\errlTwo{h} = \left[\sum\limits_{\bcell \in \bmesh_h}\sum\limits_{\mcell\in\mmesh(\bcell)} \left(\frac{1}{|\mcell|}\int_{\mcell} p \diff{\vect x} - p_h(\mcell)\right)^2|\mcell|\right]^\frac12,
$$
where $|\mcell|$ is the area of cell $\mcell$.

If~$\bmesh_h$ consists of triangles and no material interfaces are present, ASC($n$) boils down to mixed-hybrid Raviart\,--\,Thomas finite element method (which is algebraically equivalent to~$R\,T_0$ finite element method). In this particular case we have~\cite{M2AN_1980__14_3_249_0}
$$
	\|\vect u - \vect u_h\|_{\LTwoSpace} \le c\,h\,\|\vect u\|_{\HSpace{1}},\quad\|p - p_h\|_{\LTwoSpace} \le c \left( h\,\|p\|_{\HSpace{1}} + h^2\,\|p\|_{\HSpace{2}} \right),
$$
so one cannot expect ASC($n$) $\LTwo$-convergence to be better than linear. Note that
\begin{equation}\label{l2L2}
	\| p - p_h \|_{\lTwoSpace} \le \| p - p_h \|_{\LTwoSpace}
\end{equation}
since $\| p - p_h \|_{\lTwoSpace} = \| P_h\,(p - p_h) \|_{\lTwoSpace} \le \|P_h\|_{\mathcal L(\LTwoSpace, \mathbb V_h)} \| p - p_h \|_{\LTwoSpace}$, and the operator norm~$\|P_h\|_{\mathcal L(\LTwoSpace, \mathbb V_h)} = 1$ by Pythagorean theorem. Thus one may expect some improvement in $\lTwo$-convergence as one increases~$n$ for ASC($n$).

@@

\begin{figure}[h]
	\centering
	\begin{subfigure}{.41\linewidth}
		\centering
		\includegraphicsw{err2_asc0.png}
		\caption{$\vect K_1 \equiv \vect K_2 \equiv \vect I$}
		\label{fig:fake:2}
	\end{subfigure}%
	\hfill
	\begin{subfigure}{.41\linewidth}
		\centering
		\includegraphicsw{err3_asc0.png}
		\caption{$\vect K_1 \equiv \vect K_2 \equiv \vect K_3 \equiv \vect I$}
		\label{fig:fake:3}
	\end{subfigure}
	\caption{Material distribution for pseudo-multi-material problem: two materials (left), three materials (right)
	\label{fig:fake}}		
\end{figure}

The first set of tests is designed to check the property of the method to accurately recover the solution that is the polynomial of degree~1. Let us consider the diffusion problem~\eqref{dual} with~$c \equiv f \equiv 0$, $\partial\Omega_D = \partial\Omega$. The computational domain $\Omega=(0,1)^2$ is divided into several subdomains by non-intersecting straight lines. In these settings the interface reconstruction algorithm MOF reconstructs the interfaces exactly. To test the {\it linearity preservation} property, we set up a pseudo-multi-material problem with the diffusion tensor being the same in all subdomains, $\vect K_i = \vect I$. The exact solution a linear function. The geometry of two cases under consideration is shown in Figure~\ref{fig:fake}.

We denote the solution computed  with the ASC($n$) method by~$p_{h,\,n}$, $n = 0, 1$. For ASC(0) we have~$\errlTwo{h,\,0} = 6.38 \times 10^{-2}$ and $6.41 \times 10^{-2}$ for the configurations shown in Figures~\ref{fig:fake:2} and~\ref{fig:fake:3}, respectively. That is, ASC(0) is not able to recover $P_1$ solutions exactly.

Since ASC(1) approximates interface traces with $P_1$ functions it recovers edge-based degrees of freedom exactly in the sense of mean values. This results in exact reconstruction of cell-based unknowns and {\it linearity preservation} property for both examples, i.e.
\begin{equation*}
	\errlTwo{h,\,1} = \left\| p - p_{h,\,1} \right\|_{\lTwoSpace} = 0.
\end{equation*}
% As we saw in previous section,
%In general, one may not expect concentration and flux convergence to be better than second order with respect to~$\lTwo$\,--\,error for ASC($1$).  However, taking the example above into account, one may expect that convergence of ASC(1) with respect to~$\lTwo$-norm is superior
%to  convergence properties of ASC(0).

@@

In this set of tests, we consider the diffusion problem~\eqref{dual} with~$c \equiv f \equiv 0$, $\partial\Omega_D = \partial\Omega$, and two different materials in the domain. $\vect K = k\,\vect I$, $k = 1$ in the left part of the domain and $k = 0.1$ in the right (see Figure~\ref{fig:pwlin:mat}). The exact solution is piecewise linear such that the normal flux is continuous across the interface (see Figure~\ref{fig:pwlin:p}).

@@

For this example we use a sequence of square base\,meshes~$\bmesh_{h_i}$, $i = 1, 2, 3, 4$. We denote by
\begin{equation*}
	\rho_{h_i,\,n} \coloneqq \frac{\ln \errlTwo{h_i,\,n} / \errlTwo{h_{i+1},\,n}}{\ln h_i / h_{i+1}}
\end{equation*}
the reduction rate order of ASC($n$) in~$\lTwo$-norm between $i$th and $(i+1)$th refinement steps. We also compute the $\ell^{\infty}$-norm of the error
\begin{equation*}
	\errInf{h_i,\,n} \coloneqq \left\| p - p_{h_i,\,n} \right\|_\infty
\end{equation*}
for ASC($n$).

\begin{table}[h!]
	\centering
	\caption{Piecewise linear example: convergence \label{fig:conv:pwlin}}
	\footnotesize
	\begin{tabular}[1.5]{| c | c || c | c || c |}
		\hline
		\multirow{5}{*}{\rotatebox{90}{ASC(0)}} & $h$ & $\errlTwo{0}$ & $\rho$ & $\errInf{0}$ \\
		\cline{2-5}
		& $3.5\times10^{-1}$ & $7.3\times10^{-1}$ & & 4.8 \\
		\cline{2-5}
		& $8.8\times10^{-2}$ & $1.6\times10^{-1}$ & 1.1 & 1.2 \\
		\cline{2-5}
		& $2.2\times10^{-2}$ & $3.7\times10^{-2}$ & 1.1 & $3.4\times10^{-1}$ \\
		\cline{2-5}
		& $5.5\times10^{-3}$ & $8.9\times10^{-3}$ & 1.0 & $7.9\times10^{-2}$ \\
		\hline
		\hline
		\multirow{5}{*}{\rotatebox{90}{ASC(1)}} & $h$ & $\errlTwo{1}$ & $\rho$ & $\errInf{1}$ \\
		\cline{2-5}
		& $3.5\times10^{-1}$ & $2.5\times10^{-2}$ & & $1.6\times10^{-1}$ \\
		\cline{2-5}
		& $8.8\times10^{-2}$ & $1.9\times10^{-3}$ & 1.84 & $6.3\times10^{-2}$ \\
		\cline{2-5}
		& $2.2\times10^{-2}$ & $1.6\times10^{-4}$ & 1.79 & $9.8\times10^{-3}$ \\
		\cline{2-5}
		& $5.5\times10^{-3}$ & $1.3\times10^{-5}$ & 1.80 & $4.0\times10^{-3}$ \\
		\hline
	\end{tabular}
\end{table}

Numerical results are shown in Table~\ref{fig:conv:pwlin}. We observe that ASC(0) converges linearly with respect to the $\lTwo$-norm, and ASC(1) has the convergence rate close to quadratic with respect to the $\lTwo$-norm.

@@

\subsubsection{Two materials}\label{sec:twomat}

@@

Let us consider the diffusion problem~\eqref{dual} with~$c \equiv 0$, $\partial\Omega_D = \partial\Omega$. The computational domain is divided into subdomains: $\Omega_1 = \{ {\bf x} : \|{\bf x} - {\bf x}_0\|< 0.2\}$ with~${\bf x}_0 = (0.5,0.5)$ and $\Omega_2 = (0,1)^2 \setminus \bar{\Omega}_1$. The diffusion tensor is set to be $\vect K_i = k_i\,\vect I$ in $\Omega_i$, $k_1 = 0.001$ and $k_2=1$. The exact solution is piecewise quadratic such that the normal flux is continuous across the interface (see Figure~\ref{fig:pwquad2}). For this problem we compare convergence properties of the  ASC(0) and ASC(1) methods on a sequence of Voronoi meshes.

\begin{table}[h!]
	\centering
	\caption{Piecewise quadratic example, two materials: convergence \label{tab:conv:pwquad2}}
	\footnotesize
	\begin{tabular}[1.1]{| c | c || c | c || c |}
		\hline
		\multirow{7}{*}{\rotatebox{90}{ASC(0)}} & $h$ & $\errlTwo{0}$ & ${\rho}$ & $\errInf{0}$ \\
		\cline{2-5}
		& $3.0\times10^{-1}$ & $2.4\times10^{-3}$ & & $6.3\times10^{-1}$ \\
		\cline{2-5}
		& $1.5\times10^{-1}$ & $6.5\times10^{-4}$ & 2.0 & $7.0\times10^{-3}$ \\
		\cline{2-5}
		& $8.1\times10^{-2}$ & $2.6\times10^{-4}$ & 1.4 & $3.2\times10^{-3}$ \\
		\cline{2-5}
		& $4.2\times10^{-2}$ & $1.4\times10^{-4}$ & 0.9 & $2.3\times10^{-3}$ \\
		\cline{2-5}
		& $2.1\times10^{-2}$ & $3.7\times10^{-5}$ & 1.9 & $1.1\times10^{-3}$ \\
		\cline{2-5}
		& $1.0\times10^{-2}$ & $2.7\times10^{-5}$ & 0.4 & $8.6\times10^{-4}$ \\
		\hline
	\end{tabular}
	\begin{tabular}[1.1]{| c | c || c | c || c |}
		\hline
		\multirow{7}{*}{\rotatebox{90}{ASC(1)}} & $h$ & $\errlTwo{1}$ & ${\rho}$ & $\errInf{1}$ \\
		\cline{2-5}
		& $3.0\times10^{-1}$ & $2.4\times10^{-3}$ & & $2.1\times10^{-3}$ \\
		\cline{2-5}
		& {$1.5\times10^{-1}$} & $7.0\times10^{-4}$ & 1.9 & {$1.3\times10^{-2}$} \\
		\cline{2-5}
		& $8.1\times10^{-2}$ & $2.3\times10^{-4}$ & 1.8 & $6.8\times10^{-4}$ \\
		\cline{2-5}
		& $4.2\times10^{-2}$ & $6.8\times10^{-5}$ & 1.8 & $3.2\times10^{-4}$ \\
		\cline{2-5}
		& $2.1\times10^{-2}$ & $2.0\times10^{-5}$ & 1.8 & $1.1\times10^{-4}$ \\
		\cline{2-5}
		& $1.0\times10^{-2}$ & $5.4\times10^{-6}$ & 1.9 & $3.3\times10^{-5}$ \\
		\hline
	\end{tabular}
\end{table}

@@

We also observe a bump in the max norm error for ASC(1) on the second mesh level, $h = 1.5\times10^{-1}$. To have some insight, we show the corresponding mesh in the Figure~\ref{fig:conv:pwquad2:inf:mesh}. One may note that the interface reconstruction produces significant discontinuity of interfaces: A small volume of the external material, i.e. the one occupying $\Omega_2$ domain, appears inside the disk (domain $\Omega_1$). Due to constant trace approximation, ASC(0) is not sensitive to such irregularity. It turns out that for ASC(1) the $\ell^\infty$ norm of the error is affected by the appearance of such small isolated cut cells. At the same time, this does not affect the $\lTwo$-convergence of ASC(1).

\begin{figure}[h]
	\centering
	\label{fig:conv:pwquad2:inf}
	\begin{subfigure}{.29\linewidth}
		\centering
		\includegraphicsw{circle_voronoi_2_mat.png}
		\caption{Materials}
		\label{fig:conv:pwquad2:inf:mesh}
	\end{subfigure}%
	\hskip .6cm
	\begin{subfigure}{.33\linewidth}
		\centering
		\includegraphicsw{circle_voronoi_2_asc0.png}
		\caption{ASC(0), $p_h$}
	\end{subfigure}%
	\hskip1ex
	\begin{subfigure}{.33\linewidth}
		\centering
		\includegraphicsw{circle_voronoi_2_asc1.png}
		\caption{ASC(1), $p_h$}			
	\end{subfigure}%
	\caption{Piecewise quadratic example, two materials: $h = 1.5\times10^{-1}$. This figure illustrates the appearance of small isolated material volumes during numerical reconstruction of material interfaces. This may affect the $\ell^\infty$ error norm of the ASC(1)}
\end{figure}

\subsubsection{Three materials}\label{sec:threemat}

@@

In the next group of numerical tests, we consider the same  diffusion problem~\eqref{dual} with~$c \equiv 0$, $\partial\Omega_D = \partial\Omega$. The computational domain is now divided into three subdomains: $\Omega_1 = \{{\bf x} : \|{\bf x} - {\bf x}_0\| < 0.15\}$, $\Omega_2 = \{{\bf x} : 0.15 < \|{\bf x} - {\bf x}_0\| < 0.2\}$, and $\Omega_3 = (0,1)^2 \setminus (\bar{\Omega}_1\cup\bar{\Omega}_2)$. The diffusion tensor is set to be $\vect K_i = k_i\,\vect I$, $k_{1} = k_{3} = 1$, $k_2 = 0.001$. The geometry represents a ring with $k_2=0.001$ inside the ring and $k_{1} = k_{3} = 1$ outside the ring. The exact solution is piecewise quadratic such that the normal flux is continuous across the interface; see Figure~\ref{fig:pwquad3}. We use a sequence of triangular meshes to study convergence for this example. In this set of tests, we also consider the numerical method based on homogenization techniques for the comparison. The homogenization method we use is from \cite{dawes2013solving}. The homogenized values of the diffusion tensor are computed on the base cells $\bcell$ and then plugged into the MFD discretization applied on the  base mesh $\bmesh_h$; see \cite{kikinzon2017approximate} for implementation details of this method.

\begin{table}[h]
	\centering
	\caption{Piecewise quadratic example, three materials: error norms and convergence rates\label{fig:conv:pwquad3}}
	\footnotesize
	\begin{tabular}[1.1]{| c | c || c | c || c |}
		\hline
		\multirow{7}{*}{\rotatebox{90}{ASC(0)}} & $h$ & $\errlTwo{0}$ & $\rho$ & $\errInf{0}$ \\
		\cline{2-5}
		& $3.0\times10^{-1}$ & 4.5 & & 17 \\
		\cline{2-5}
		& $2.5\times10^{-1}$ & 4.5 & & 17 \\
		\cline{2-5}
		& $1.3\times10^{-1}$ & 4.0 & & 17 \\
		\cline{2-5}
		& $8.3\times10^{-2}$ & 4.4 & & 17 \\
		\cline{2-5}
		& {$6.7\times10^{-2}$} & $7.1\times10^{-1}$ & & 4.9 \\
		\cline{2-5}
		& $4.3\times10^{-2}$ & $4.5\times10^{-1}$ & 1.2 & 5.0 \\
		\hline
		\hline
		\multirow{7}{*}{\rotatebox{90}{ASC(1)}} & $h$ & $\errlTwo{0}$ & $\rho$ & $\errInf{0}$ \\
		\cline{2-5}
		& $3.0\times10^{-1}$ & $4.5\times10^{-1}$ & & 3.5 \\
		\cline{2-5}
		& $2.5\times10^{-1}$ & $2.6\times10^{-1}$ & 3 & 2.7 \\
		\cline{2-5}
		& $1.3\times10^{-1}$ & $9.2\times10^{-2}$ & 1.5 & $6.2\times10^{-1}$ \\
		\cline{2-5}
		& $8.3\times10^{-2}$ & $4.8\times10^{-2}$ & 1.6 & $8.3\times10^{-1}$ \\
		\cline{2-5}
		& $6.7\times10^{-2}$ & $2.8\times10^{-2}$ & 2.5 & $2.3\times10^{-1}$ \\
		\cline{2-5}
		& $4.3\times10^{-2}$ & $1.0\times10^{-2}$ & 2.3 & $6.3\times10^{-2}$ \\
		\hline
	\end{tabular}
	\begin{tabular}[1.1]{c | c | c || c | c || c |}
		\cline{2-6}
	    \multirow{14}{*}{\rotatebox{90}{Homogenization}} & \multirow{7}{*}{\rotatebox{90}{Arithmetic}} & $h$ & $\errlTwo{\text{AH}}$ & $\rho$ & $\errInf{\text{AH}}$ \\
		\cline{3-6}
	    & & $3.0\times10^{-1}$ & 4.9 & & 17 \\
	    \cline{3-6}
	    & & $2.5\times10^{-1}$ & 5.0 & & 17 \\
	    \cline{3-6}
	    & & $1.3\times10^{-1}$ & 4.9 & & 17 \\
	    \cline{3-6}
	    & & $8.3\times10^{-2}$ & 4.7 & & 17 \\
	    \cline{3-6}
	    & & {$6.7\times10^{-2}$} & 4.4 & & 16 \\
	    \cline{3-6}
	    & & $4.3\times10^{-2}$ & $9.7\times10^{-1}$ & 3.5 & 5.7 \\
	    \hhline{~=====}
	    & \multirow{7}{*}{\rotatebox{90}{Harmonic}} & $h$ & $\errlTwo{\text{HH}}$ & $\rho$ & $\errInf{\text{HH}}$ \\
	    \cline{3-6}
	    & & $3.0\times10^{-1}$ & 2.3 & & 15 \\
	    \cline{3-6}
	    & & $2.5\times10^{-1}$ & 1.7 & 1.6 & 16 \\
	    \cline{3-6}
	    & & $1.3\times10^{-1}$ & $7.3\times10^{-1}$ & 1.2 & 12 \\
	    \cline{3-6}
	    & & $8.3\times10^{-2}$ & $4.8\times10^{-1}$ & 1.0 & 12 \\
	    \cline{3-6}
	    & & $6.7\times10^{-2}$ & $3.4\times10^{-1}$ & 1.6 & 9.4 \\
	    \cline{3-6}
	    & & $4.3\times10^{-2}$ & $1.6\times10^{-1}$ & 1.7 & 8.2 \\
	    \cline{2-6}
	  \end{tabular}
\end{table}

Numerical results are shown in Table~\ref{fig:conv:pwquad3}. We compare ASC(0), ASC(1), arithmetic, and harmonic homogenization. Note that up to mesh level~$h = 8.3\times10^{-2}$ macro-faces with three materials are present, and starting from {$h = 6.7\times10^{-2}$} the meshes are fine enough so that only macro-faces sharing one or two materials occur.

We see that ASC(0) starts to converge linearly with respect to $\lTwo$-norm once~$h < 6.7\times10^{-2}$. ASC(1) demonstrates a robust behavior and shows the convergence rate close to quadratic with respect to $\lTwo$-norm as in previous examples, and performs better than homogenization approaches.

\subsection{Algebraic robustness}
%
%	One may expect that the conditioning of the ASC($n$) system~\eqref{asc_system} gets worse as one increases~$n$. In fact, we have the following result.\\
%	\begin{theorem}\label{thm:eig}
%		Let~$\mu_{\text{min}}^n > 0$ be the minimal eigenvalue of the system matrix~$\vect S_\bmesh$ in~\eqref{asc_system} of the ASC($n$) method. Then we have
%		\begin{equation}\label{mineig}
%			\mu_{\text{min}}^1 < \mu_{\text{min}}^0.
%		\end{equation}
%	\end{theorem}
%	\begin{proof}
%		\Sasha{We have it. To be added.}
%	\end{proof}
%
%	\Sasha{We also believe that the max eig value stays the same (based on num experiments), i.e. $\mu_{\text{max}}^1 \approx \mu_{\text{max}}^0$ or even $\mu_{\text{max}}^1 = \mu_{\text{max}}^0$}. I think it would be nice to prove it here, so we can show that the cond number is governed by the smallest eig value alone.
%	
In this section, we study the dependence of the condition number of matrix $\vect S_\bmesh$ on the position of the material interface against the background mesh. For this purpose, we solve the diffusion problem~\eqref{dual} in the unit square with $\partial\Omega = \partial\Omega_D$, $\vect K = k\,\vect I$, $k = 1$ on the left part and $k = 0.1$ on the right. We keep the mesh fixed, and change the position of the interface so that the minimal length of mini-faces~$w$ gets smaller, $w = 10^{-1}, 10^{-2}, \dots, 10^{-5}$ (see Figure~\ref{fig:w}).
